---
title: "Manual reference retrieval"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{manual_fetch}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

If you are here, this is because you want to manually retrieve a list of reference, outside of the automated task that you might have set up after reading [LitFetchR (Tutorial)](https://thomasdumond.github.io/LitFetchR/articles/LitFetchr.html).

## Setup
From your individual review R directory, load `LitFetchR`:
```{r, eval = FALSE}
library(LitFetchR)
```

## Manual reference retrieval
Make sure to have save your search string using `create_save_search()` as the following function need to access the file *search_list.txt*, see [LitFetchR (Tutorial)](https://thomasdumond.github.io/LitFetchR/articles/LitFetchr.html).

```{r, eval=FALSE}
manual_fetch(WOS = TRUE, SCP = TRUE, PMD = TRUE)
```

After running `manual_fetch()`, new unique *history_dedup_* and *citationCSV_* files are created and *history_id* is updated.
