---
title: "Remove or change a scheduled task"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{remove_task}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

If you are here, this is because you want to remove or modify a reference retrieval task that you set up earlier. Otherwise, check the article [LitFetchR (Tutorial)](https://thomasdumond.github.io/LitFetchR/articles/LitFetchr.html) to learn how to set up a task.

## Setup
From your individual review R directory, load `LitFetchR`:
```{r, eval = FALSE}
#Load LitFetchR
library(LitFetchR)
```

## Remove a scheduled task

Just use the following function with the name of the scheduled task:

```{r, eval=FALSE}
#Load LitFetchR
library(LitFetchR)

#remove a scheduled task using its name/identification
remove_scheduled_task("taskID")

#Example of what you should see:
# > remove_scheduled_task("fish_vibrio")
# SUCCESS: The scheduled task "fish_vibrio" was successfully deleted.
# Windows task 'fish_vibrio' removed (or did not exist).

```

## Modify a scheduled task
There is no function to directly modify a scheduled task at the moment. You can simply:

1. Remove the scheduled task (see above)
2. Setup a new task &rarr; see [LitFetchR (Tutorial)](https://thomasdumond.github.io/LitFetchR/articles/LitFetchr.html)
